Working Script

### 2023-01-03 ArchivedCode/MsCcHSFeedOutlineDec15.Rmd
Moved scripts for submission

```{r}
barsdead <- ggplot(data = datadead, aes(x = treatment, fill = fate)) + 
  theme_bw() + 
  geom_bar(position = "fill") + 
  facet_wrap(~food) + 
  scale_y_continuous(breaks = c(0, .25, .5, .75, 1), limits = c(0, 1.07)) + 
  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome") + 
  scale_fill_manual(values = c("purple", "#1E88E5", "lime green", "orange", "#D81B60"),
                    labels = c("Died", "Wander", "WE", "Small WOWE", "Large WOWE")) + 
  geom_text(data = samplesize, aes(x = x, y = y, label = N))

@@

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/outcomesdead.png", plot = barsdead, width = 8, height = 5)
```

>>>>

```{r}
barsdead <- ggplot(data = datadead, aes(x = treatment, fill = fate)) + 
  theme_bw() + 
  geom_bar(position = "fill") + 
  facet_wrap(~food) + 
  scale_y_continuous(breaks = c(0, .25, .5, .75, 1), limits = c(0, 1.07)) + 
  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome") + 
  scale_fill_manual(values = c("dead" = "purple", "wander" = "#1E88E5" , "em" = "lime green", 
                                       "wowe" = "orange", "wowe mongo" =  "#D81B60"),
                    labels = c("Died", "Wander", "WE", "Small WOWE", "Large WOWE")) + 
  geom_text(data = samplesize, aes(x = x, y = y, label = N))

@@

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/outcomesdead.png", barsdead, width = 8, height = 5)
```

*Note: Could not get the legend to stop labelling in alphabetical order, so I will switch colors in Photoshop :( *

### 2023-01-03 ArchivedCode/WorkingScript.Rmd
Moved scripts for submission

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
```

@@

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedSep15modfinal.csv")
```

@@

```{r}
ggplot(data, aes(x = mass.max, y = area)) + 
  geom_point(aes(color = food)) + 
  labs(x = "Maximum mass achieved (mg)", y = "Leaf surface area consumed (cm2)", color = "Food type")
```

```{r}
ggplot(data, aes(x = mass.max, y = area)) + 
  geom_point(aes(color = fate))
```

@@

@@

@@

>>>>

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
library(lubridate)
```

@@

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedNov30modfinal.csv")
```

@@

```{r}
ggplot(data, aes(x = mass.max, y = area)) + 
  theme_bw() + 
  geom_point(aes(color = food)) + 
  labs(x = "Maximum mass achieved (mg)", y = "Leaf surface area consumed (cm2)", color = "Food type")
```

```{r}
ggplot(data, aes(x = mass.max, y = area)) + 
  theme_bw() + 
  geom_point(aes(color = fate, shape = food)) + 
  #scale_color_viridis_d() + 
  scale_shape_manual(values = c(19,6)) + 
  labs(x = "Maximum mass achieved (mg)", y = "Leaf surface area consumed (cm2)")
```
```{r}
data <- data[data$fate != "wander*", ]

modfate <- lmer(mass.max ~ fate*food + (1|bin), data = data)

summary(modfate)
```

```{r}
ggplot(data, aes(x = mass.max, y = area)) + 
  theme_bw() + 
  geom_point(aes(color = treatment)) + 
  scale_color_viridis_d() + 
  labs(x = "Maximum mass achieved (mg)", y = "Leaf surface area consumed (cm2)", color = "Treatment")
```

@@

```{r}
mod1.9 <- lm(area ~ food*para*HS, data = data)

summary(mod1.9)
```

@@

```{r}
mod3.5 <- lm(mass.max ~ area, data = data )

summary(mod3.5)
```

@@

## Age vs. Mass plots

```{r}
# Internal process of the loop to convert days to dates
expt_day <- function(start.date, date){
  date <- mdy(date)
  start <- mdy(start.date)
  diff <- yday(date) - yday(start)

  return(diff)
}

# Code for the loop itself
loop <- function(start.date, date.list){
  days <- rep(NA, length(date.list))
  for (i in 1:(length(days))){
    days[i] <- expt_day(start.date = start.date, date = date.list[i])
  }
  return(days)
}

# Convert all the dates to days

data$day.hatch <- loop(start.date = "07/12/2020", date.list = data$date.hatch)
data$day.3rd <- loop(start.date = "07/12/2020", date.list = data$date.3rd)
data$day.4th <- loop(start.date = "07/12/2020", date.list = data$date.4th)
data$day.5th <- loop(start.date = "07/12/2020", date.list = data$date.5th)
data$day.w <- loop(start.date = "07/12/2020", date.list = data$date.w)
data$day.remove <- loop(start.date = "07/12/2020", date.list = data$date.remove)
#data$day.5th.2 <- loop(start.date = "07/12/2020", date.list = data$date.5th.2)
#data$day.5th.3 <- loop(start.date = "07/12/2020", date.list = data$date.5th.3)
#data$day.5th.4 <- loop(start.date = "07/12/2020", date.list = data$date.5th.4)
#data$day.6th <- loop(start.date = "07/12/2020", date.list = data$date.6th)
#data$day.6th.2 <- loop(start.date = "07/12/2020", date.list = data$date.6th.2)
#data$day.6th.3 <- loop(start.date = "07/12/2020", date.list = data$date.6th.3)
#data$day.7th <- loop(start.date = "07/12/2020", date.list = data$date.7th)
#data$day.7th.2 <- loop(start.date = "07/12/2020", date.list = data$date.7th.2)
#data$day.7th.3 <- loop(start.date = "07/12/2020", date.list = data$date.7th.3)
data$day.max <- loop(start.date = "07/12/2020", date.list = data$date.max)
```

```{r}
# Time til each instar
data$tth <- 0
data$tt3 <- data$day.3rd - data$day.hatch
data$tt4 <- data$day.4th - data$day.hatch
data$tt5 <- data$day.5th - data$day.hatch
data$ttw <- data$day.w - data$day.hatch
data$ttrem <- data$day.remove - data$day.hatch
data$ttmax <- data$day.max - data$day.hatch

# Mass at each instar -> natural log of mass

data$lnh <- log(data$mass.hatch)
data$ln3 <- log(data$mass.3rd)
data$ln4 <- log(data$mass.4th)
data$ln5 <- log(data$mass.5th)
data$lnw <- log(data$mass.w)
data$lnrem <- log(data$mass.remove)
data$lnmax <- log(data$mass.max)

```{r}
masslong <- data %>% gather(instar, mass, mass.3rd, mass.4th, mass.5th, mass.max)
masslong$instar <- gsub("mass.", "", masslong$instar)
masslong$instar <- gsub("rd", "", masslong$instar)
masslong$instar <- gsub("th", "", masslong$instar)

agelong <- data %>% gather(instar, age, tth, tt3, tt4, tt5, ttmax)
agelong$instar <- gsub("tt", "", agelong$instar)

masslong <- masslong %>% select(ID, treatment, food, instar, mass)
agelong <- agelong %>% select(ID, treatment, food, instar, age)

datalong <- merge(masslong, agelong, by = c("ID", "treatment", "food", "instar"))

```{r}
lnmasslong <- data %>% gather(instar, mass, lnh, ln3, ln4, ln5, lnw, lnrem, lnmax)
lnmasslong$instar <- gsub("ln", "", lnmasslong$instar)

lnmasslong <- lnmasslong %>% select(ID, treatment, instar, mass)

lndatalong <- merge(lnmasslong, agelong, by=c("ID", "treatment", "instar"))
```

```{r}
devplot <- ggplot(datalong, aes(x = age, y = mass, group = ID, color = treatment, shape = food)) + 
  theme_bw() + 
  geom_point() +
  scale_shape_manual(values = c(1, 19)) + 
  geom_line(aes(linetype = food), alpha = 0.5) + 
  scale_linetype_manual(values = c("dotdash", "solid")) + 
  scale_color_viridis_d() + 
  labs(x = "Developmental age (days)", y = "Mass gained (mg)", shape = "Hostplant", linetype = "Hostplant", 
       color = "Treatment group")

devplot
```

```{r}
lndevplot <- ggplot(lndatalong, aes(x = age, y = mass, group = ID, color = treatment)) + 
  geom_point() +
  geom_line(alpha = 0.5) + 
  scale_color_viridis_d() + 
  labs(x = "Developmental age (days)", y = "Natural log of mass gained")

lndevplot
